\sectiontitle{Other Peer--reviewed articles}
\begin{enumerate}[leftmargin = 1.5em, start = 4]
\item Fonsah, E.G., \& \textbf{Kunwar, S.R.} (2024). \href{https://juniperpublishers.com/artoaj/pdf/ARTOAJ.MS.ID.556416.pdf}{Economics of Satsuma Citrus Production Using Drip Irrigation and Frost Protection in the United States.} \textit{Agricultural Research \& Technology}, 28(4):1-11.

\item Fonsah, E. G., \textbf{Kunwar, S. R.}, \& Diaz-Perez, J. C. (2023). \href{https://internationalscholarsjournals.org/articles/7533205004012023}{Economic Evaluation of Bell Pepper Production Under Colored Shade Nets System in the Southeast Region of the USA.} \textit{African Journal of Agricultural Economics and Rural Development}, 11(1), 001-007.
    
\item Bogati, S., \textbf{Kunwar, S. R.}, \& Amgain, L. P. (2021). \href{https://doi.org/10.1016/j.heliyon.2021.e08096}{Assessment of Nutrient Expert\textsuperscript{\textregistered}-Hybrid Maize Model on Productivity and Profitability of Winter Maize in Terai Region of Eastern Nepal.} \textit{Heliyon}, 7(10), e08096.

\item \textbf{Kunwar, S. R.}, Fonsah, E. G., \& Ramirez, O. (2021). \href{https://doi.org/10.22004/ag.econ.313450}{Understanding Profitability of Georgia Blueberry Growers Adopting a Stochastic Approach.} \textit{Journal of Food Distribution Research}, 52(856-2021-1301), 39-45.
    
\item \textbf{Kunwar, S. R.}, Bogati, S., Fonsah, E.G., \& Amgain, L.P. (2019). \href{https://doi.org/10.5296/jas.v7i3.14900}{Economic Assessment of Adopting Nutrient Expert\textsuperscript{\textregistered} Wheat Model Vs Conventional Wheat Fertilizer Application Management in Morang, Nepal.} \textit{Journal of Agricultural Studies}, ISSN: 2166-0379, Vol 7(3): 38-48.

\end{enumerate}